---
title: "Lab Assignment Questions"
format: html
echo: false
---


{{< var Lab.assignments.quizInfo >}}

# Rubric

{{< var Lab.assignments.rubricInfo >}}

```{r include=FALSE}

library(knitr)
```

```{r}
#| label: tbl-schedule
#| tbl-cap: "Lab Quiz Rubric"
#| tbl-colwidths: [10,35,35,10]

rubric <- read.csv(file = '../sheets/Rubric.csv',sep='|')
kable(rubric, col.names = gsub("[.]", " ", names(rubric)))

```

# Quiz Questions

## Part 1

(@) Upload your *Central_Wellington_Layout.pdf*. [**Hint**](instructions.qmd#make-your-first-map)


(@) What does the select layer by attributes tool do? [**Hint**](instructions.qmd#explore-your-data)

- Find features that meet specific criteria.
- Find features that are in a specific area.
- Find features based on their spatial relationship to other features.

(@) A ______ in ArcGIS Pro is a way to put a map on a page and map elements like a north arrow, legend, scale bar, and extent indicator. [**Hint**](instructions.qmd#make-a-layout)

- Map frame
- Layout
- Data view
- Geoprocessing pane


(@) What tool was used to create the 1500 meter zone around the campsites? [**Hint**](instructions.qmd#use-geoprocessing-tools)

- Select by location
- Buffer
- Intersect
- Select by attribute

(@) What is the first step when creating a new point layer? [**Hint**](instructions.qmd#create-points-on-a-map)

- Create a polygon feature class in the project geodatabase
- Create a raster dataset
- Make sure you are zoomed into your area of interest. 
- Create point feature class in the project geodatabase

## Part 2

(@) A ______ is a file management structure that is unique to ESRI products. [**Hint**](instructions.qmd#Geodatabases)

- Folder
- Zipfile
- Shapefile
- Geodatabase

(@) In your own words, what does georeferencing do? [**Hint**](instructions.qmd#georeferencing)

(@) How many cholera deaths were recorded in this outbreak? ______ How many locations (points) are in the dataset? ______ What is the highest number of deaths at one location? ______ [**Hint**](instructions.qmd#inspect-the-data)

(@) ______ point symbols are sized differently to convey magnitude/intensity. [**Hint**](instructions.qmd#symbolize-by-count)

- Triangular
- Sequential
- Graduated
- Bigger


(@) What do the mean center and directional distribution tell us about a set of points? [**Hint**](instructions.qmd#measures-of-central-tendency)

(@) Why might Kernel Density be more useful for identifying the source of a source(s) of a cholera outbreak outbreak than the mean center and directional distribution? [**Hint**](instructions.qmd#kernel-density)


(@) Upload your *Kernel_Density.pdf*. [**Hint**](instructions.qmd#kernel-density)
