---
title: "Lab Assignment Questions"
format: html
echo: false
---


{{< var Lab.assignments.quizInfo >}}

# Rubric

{{< var Lab.assignments.rubricInfo >}}

```{r include=FALSE}

library(knitr)
```

```{r}
#| label: tbl-schedule
#| tbl-cap: "Lab Quiz Rubric"
#| tbl-colwidths: [10,35,35,10]

rubric <- read.csv(file = '../sheets/Rubric.csv',sep='|')
kable(rubric, col.names = gsub("[.]", " ", names(rubric)))

```

# Quiz Questions

## Part 1

### Exercise 1

(@) Metadata is _____ about ____. [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise1-discover-coord.html#inspecting-the-metadata)

### Exercise 2

(@) In your own words, what does Project “On the Fly” do? [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise2-transform.html#exercise-2-projecting-on-the-fly)

(@) What UTM zone is Vancouver in?. [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise3-project.html#exercise-3-project-your-data)

* 10 S
* 11 N
* 10 N
* 18 N


### Exercise 3

(@) Use the [What UTM Zone am I in?](https://mangomap.com/robertyoung/maps/69585/what-utm-zone-am-i-in-#) tool match find the UTM zones for these cities:

- Inuvik, NWT, Canada
- Cape Town, South Africa
- Kyoto, Japan


### Exercise 4

(@) What spatial unit is the Shape_Area of the CAN_albersEA in? (Check the Spatial Reference Info). [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise4-pop-density.html#inspect-the-attribute-tables)

* Kilometers
* Meters
* Square Miles
* Square Kilometers
* Square Meters
* Degrees

(@) What is the difference in Shape_Area given for the CAN_webMercator and CAN_albersEA layers in **Square Kilometers**?  Round to the nearest whole number. [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise4-pop-density.html#inspect-the-attribute-tables)

- Folder
- Zipfile
- Shapefile
- Geodatabase

(@) We are multiplying by 1000000 to convert the units to population per square ____. [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise4-pop-density.html#calculating-population-density)

(@) What is the population density of the **CAN_webMercator** layer? Round your answer to the nearest hundredth place. [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise4-pop-density.html#calculating-population-density)

(@) What is the population density of the **CAN_albersEA** layer? Round your answer to the nearest hundredth place. [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise4-pop-density.html#calculating-population-density)

(@) How do the calculations compare?  Which layer do you think has the most accurate Population Density and why? [**Hint**](https://ubc-library-rc.github.io/map-projections/content/exercise4-pop-density.html#calculating-population-density)


## Part 2

(@) Submit your figure showing Canada in the four different coordinate systems. [**Hint**](instructions.qmd#four-ways-to-display-canada)

(@) Write a **paragraph or two** comparing and contrasting the four different coordinate systems.  What are the differences/similarities between them?  If you wanted to make a map of population totals by province, which coordinate system(s) would you choose? What if you wanted to make a map of population **density** by province, which coordinate system(s) would you choose? [**Hint**](instructions.qmd#four-ways-to-display-canada)

